### 2015-01-21 paper_10_intro.tex
capitalize some table and image names

    Software development organizations need a framework to define
    what measurements should be tracked and how those measurements
    should be reported.  The MPI framework provides a solid foundation
    for a consistent evaluation.  It should also provide a broad
    view of the overall organization.  It is common for software development
    organizations to measure and focus soley on the source code
    being produced.  However, a software development organization does more
    than just produce source code.  There is documentation to be
    written, testcases to be created, systems to be deployed, and
    decisions to be made.  The framework provides an evaluation
    of the overall software development organization.

@@

    \begin{figure}[ht]
        \centering
        \includegraphics[scale=.7]{images/cmmi.png}
        \caption[Characteristics of CMMI]{Characteristics of CMMI, 
            image adapted from  \cite{Godfrey} }
        \label{fig:cmmi}
    \end{figure}

>>>>

    Software development organizations need a framework to define
    what measurements should be tracked and how those measurements
    should be reported.  The MPI framework provides a solid foundation
    for a consistent evaluation.  MPI analyzes the historical performance
    of an SDO
    to create a baseline in order to provide a broad
    view of the overall organization.  It is common for software development
    organizations to measure and focus soley on the source code
    being produced.  However, a software development organization does more
    than just produce source code.  There is documentation to be
    written, testcases to be created, systems to be deployed, and
    decisions to be made.  The framework provides an evaluation
    of the overall software development organization, not just the
    source code.

@@

    \begin{figure}[ht]
        \centering
        \includegraphics[scale=.7]{images/cmmi.png}
        \caption[CHARACTERISTICS OF CMMI]{Characteristics of CMMI, 
            image adapted from  \cite{Godfrey} }
        \label{fig:cmmi}
    \end{figure}

### 2015-01-21 paper_20_sdo.tex
capitalize some table and image names

        \begin{figure}[ht]
            \centering
            \includegraphics[scale=.5]{images/benington_waterfall.PNG}
            \caption[Benington's original diagram for producing large software systems]
                    {Benington's original diagram for producing large software 
                        systems, adapted from \cite{Benington1987}}
            \label{fig:benington}
        \end{figure}%
        \begin{figure}[ht]
            \centering
            \includegraphics[scale=.5]{images/royce_waterfall.PNG}
            \caption[Royce's version of the waterfall model]
                {Royce's version of the waterfall model for producing software 
                        systems, adapted from \cite{Royce1987}}
            \label{fig:royce}
        \end{figure}

        The modern version of the waterfall model specifies that each phase needs 
        to be entirely completed before moving
        onto the next phase.  Some small amount of overlap is permitted and looping 
        occurs but both actions are discouraged and should be limited.  
        A modern diagram of the waterfall model can be seen in Figure \ref{fig:waterfall}.
        \begin{figure}[ht]
            \centering
            \includegraphics[scale=.6]{images/waterfall.png}
            \caption[Modern Waterfall]
                {Modern Waterfall Diagram, adapted from \cite{Hibbs2009} }
            \label{fig:waterfall}
        \end{figure}

@@

        The spiral model for software development was presented by Boehm in 1986
        \cite{Boehm1986, Boehm1988}. 
        The goal of the spiral mode of software development is very risk-driven.
        A software project will start with many small and quick iterations. 
        Each iteration will cover the following 4 basic steps. 
        \begin{enumerate}
            \item Determine Objectives
            \item Identify Risks
            \item Develop and Test
            \item Plan Next Iteration
        \end{enumerate}
        This model allows software to be built over a series of iterations
        without risking too much time or effort in any single iteration.
        Sprial requires a very adaptive management approach
        as well as flexibility of the key stakeholders \cite{Ruparelia2010}.
        It can also be difficult to identify risks that will occur in future
        iterations.
        Figure \ref{fig:spiral} provides a bit more detail on the iterations
        and the overall process. 
        \begin{figure}[here]
            \centering
            \includegraphics[scale=.5]{images/spiral_model.png}
            \caption[Spiral SDLC Model]{Spiral SDLC Model \cite{Boehm2000} }
            \label{fig:spiral}
        \end{figure}

>>>>

        \begin{figure}[ht]
            \centering
            \includegraphics[scale=.5]{images/benington_waterfall.PNG}
            \caption[BENINGTON'S ORIGINAL DIAGRAM FOR PRODUCING LARGE SOFTWARE SYSTEMS]
                    {Benington's original diagram for producing large software 
                        systems, adapted from \cite{Benington1987}}
            \label{fig:benington}
        \end{figure}%
        \begin{figure}[ht]
            \centering
            \includegraphics[scale=.5]{images/royce_waterfall.PNG}
            \caption[ROYCE'S VERSION OF THE WATERFALL MODEL]
                {Royce's version of the waterfall model for producing software 
                        systems, adapted from \cite{Royce1987}}
            \label{fig:royce}
        \end{figure}

        The modern version of the waterfall model specifies that each phase needs 
        to be entirely completed before moving
        onto the next phase.  Some small amount of overlap is permitted and looping 
        occurs but both actions are discouraged and should be limited.  
        A modern diagram of the waterfall model can be seen in Figure \ref{fig:waterfall}.
        \begin{figure}[ht]
            \centering
            \includegraphics[scale=.6]{images/waterfall.png}
            \caption[MODERN WATERFALL]
                {Modern Waterfall Diagram, adapted from \cite{Hibbs2009} }
            \label{fig:waterfall}
        \end{figure}

@@

        The spiral model for software development was presented by Boehm in 1986
        \cite{Boehm1986, Boehm1988}. 
        The goal of the spiral mode of software development is very risk-driven.
        A software project will start with many small and quick iterations. 
        Each iteration will cover the following 4 basic steps. 
        \begin{enumerate}
            \item Determine Objectives
            \item Identify Risks
            \item Develop and Test
            \item Plan Next Iteration
        \end{enumerate}
        This model allows software to be built over a series of iterations
        without risking too much time or effort in any single iteration.
        Sprial requires a very adaptive management approach
        as well as flexibility of the key stakeholders \cite{Ruparelia2010}.
        It can also be difficult to identify risks that will occur in future
        iterations.
        Figure \ref{fig:spiral} provides a bit more detail on the iterations
        and the overall process. 
        \begin{figure}[here]
            \centering
            \includegraphics[scale=.5]{images/spiral_model.png}
            \caption[SPIRAL SDLC MODEL]{Spiral SDLC Model \cite{Boehm2000} }
            \label{fig:spiral}
        \end{figure}

### 2015-01-21 paper_50_sdlc-ae.tex
adding material that had been removed for the proposal
adding some capitol letters to the section headers
most of the lit review is complete
capitalize some table and image names

The SDLC-AE would make gamification of the SDLC attainable.  Prior attempts
at gamification of the SDLC focus only on the development phase \cite{Dubois2013} \cite{Snipes2013}.

\begin{figure}[ht]
\includegraphics[scale=.7]{images/sdlc-ae.png}
\caption{SDLC Analytic Engine}
\label{fig:sdlc-ae}
\end{figure}

@@

\begin{comment}
    \subsection{Estimation}

@@

    \subsection{Requirements}
    List of: 
    \begin{description}
      \item[Title] 
      \item[Descrition]
      \item[author]
      \item[projectID]
      \item[date]
      \item[Comments] list of \\
      \begin{description}
        \item[date]
        \item[comment Text]
        \item[author]
      \end{description}
    \end{description}

    \subsection{Maintenance (Defects)}
    List of:
    \begin{description}
      \item[Project] 
      \item[Release]
      \item[description]
      \item[date Entered]
      \item[Date fixed]
      \item[Comments] list of \\
      \begin{description}
        \item[date]
        \item[comment Text]
        \item[author]
      \end{description}
    \end{description}

    \subsection{Testing}

@@

    \subsection{Development}

@@

    \subsection{Implementation}

@@

\end{comment}

>>>>

Once all the SDLC data is collected into a single place, there are many possible applications.  Software analytics
will be much easier to create and gamification will be much more easily attainable.

\begin{figure}[ht]
\includegraphics[scale=.7]{images/sdlc-ae.png}
\caption{SDLC ANALYTIC ENGINE}
\label{fig:sdlc-ae}
\end{figure}

@@

    \subsection{ESTIMATION}

@@

    \subsection{REQUIREMENTS}
    List of: 
    \begin{description}
      \item[Title] 
      \item[Descrition]
      \item[author]
      \item[projectID]
      \item[date]
      \item[Comments] list of \\
      \begin{description}
        \item[date]
        \item[comment Text]
        \item[author]
      \end{description}
    \end{description}

    \subsection{MAINTENANCE (DEFECTS)}
    List of:
    \begin{description}
      \item[Project] 
      \item[Release]
      \item[description]
      \item[date Entered]
      \item[Date fixed]
      \item[Comments] list of \\
      \begin{description}
        \item[date]
        \item[comment Text]
        \item[author]
      \end{description}
    \end{description}

    \subsection{TESTING}

@@

    \subsection{DEVELOPMENT}

@@

    \subsection{IMPLEMENTATION}

@@
